Holomorphic field theories and higher algebra

### 2024-10-12 draft.tex
oh boy some unpushed stuff

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}
\setcounter{tocdepth}{1}

@@

\def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
\def\owen#1{{\textcolor{red!50!black}{OG: {#1}}}}

@@

@@

@@

A physical motivation comes from supersymmetric field theories, 
which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a super Lie group known as a super Poincar\'e group.
%The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
%with larger $\cN$ denoting a bigger supergroup. 
Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
The relevance to this survey is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
even when they do not admit twists to TFTs \cite{CosSUSY}. 
(The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, 
but it does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.

@@

A community has formed, involving both mathematicians and physicists, to explore and exploit these relationships,
and it continues to grow as there is a lot to explore here.
Examples of efforts in this direction include \cite{PTVV}, \cite{FHK,HenKap}, \cite{CosWG2,CosYangian,CosTwistor}, \cite{CLbcov, LiVertex}, \cite{CGholography,BGKWY}, \cite{CostelloPaquette}, and \cite{BBBDN}, 
where our own background and interests (and unfortunately, our ignorance) have shaped this list.
\brian{Maybe add more...}

The material below focuses on connections with this work,
and the examples from physics have a perturbative flavor.
We will not discuss important directions like mirror symmetry, the geometric Langlands program, the BPS/CFT correspondence, Donaldson-Thomas theory, or other areas that are more global or more directly geometric,
although we expect there are rich connections with the topics we do discuss.
Not including these topics is primarily because our core theme already swelled to more pages than we expected, 
because a concise discussion of any of those topics does not yet seem possible with respect to our theme,
and because of our lack of background in these areas.
We hope the ideas surveyed here do connect profitably to these topics.

As complementary perspectives to that offered here, we recommend
\begin{itemize}
\item Kapranov's lectures \cite{KapLect} on factorization algebras in algebraic geometry,
\item Costello's lectures \cite{CosScheim} on how holomorphic field theories emerge from supersymmetric theories, and
\item a recent survey \cite{GKW} for physicists on how higher algebra appears in perturbative QFT, with a strong emphasis on the holomorphic examples.
\end{itemize}
Reading these would give a more well-rounded view of the subject and its possibilities.

@@

\subsection{About Manin and his influence}

Yuri Manin was a pioneer into this intellectual region where field theory, complex geometry, and homotopical algebra meet,
and his work --- beyond the beautiful results --- also gestured at rich possibilities for novel and powerful forms of geometry and physics and algebra,
summoning these possibilities towards their current unfolding today into derived geometry and operadic structures in a broad sense.
We quote \cite{ManFrob} in our epigraph, which synthesizes stacks and operads and Frobenius structures into a beautiful and coherent view on mirror symmetry.
His \cite{ManGauge} is rich with deep reformulations of supersymmetric field theory that connect it to complex geometry,
and it is a source of many inspirations;
we are also quite fond of \cite{BeiMan, ManNewDim} from roughly the same era.
Anyone interested in mathematics and physics and, especially, their relationship will delight in~\cite{ManMP}.

Beyond his writing, however, we have also benefited throughout our careers from the attitudes and atmosphere that his persona modeled and spread among mathematicians:
a generosity with ideas but also poetry and literature, an exquisite care and sensitivity to organizing and explaining mathematics (and much else),
and a kindness in conversation, where he brought his whole attention to you.
While a graduate student at Northwestern, 
OG had the unbelievable luck to overlap with Manin and thus to take several courses and have many conversations with him, 
getting to witness the personification of the Platonic idea of mathematician as intellectual.
We both spent extensive time, for example, at the Max Planck Institute for Mathematics,
which is suffused with his spirit.
We wish we had the chance to discuss the ideas from this survey with Manin;
we offer it as a small gift in gratitude for all he shared with us.

@@

In physics, a classical field theory is usually described in terms of a few pieces of data:
\begin{itemize}
\item a manifold $M$ that plays the role of ``spacetime,''
\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
\item a system of partial differential equations (PDE) for the fields, known as the equations of motion.
\end{itemize}
These equations of motion are variational: 
they are the Euler-Lagrange equations of an action functional on the space of fields,
so that solutions to these PDE are the critical points, in a sense, of some function.
In practice an action functional is a formal expression, 
written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
A few examples will illuminate this sketch.

@@

For a systematic introduction to classical field theory, 
in a style amenable to a complex geometer,
we suggest \cite{DeligneFreed}.
Recently there is an effort to revisit field theory with insights from derived geometry.
See \cite{AlfonsiYoung} for motivation and overview, 
but for a detailed development, see \cite{Steffens23, Steffens24}.
In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
(i.e., studying formal deformations of a fixed solution to the equations of motion),
which we will use to produce examples of higher algebras.

\subsection{More examples}
\label{sec: ex of theories}

@@

There are holomorphic versions of all these basic types, 
and we now spell out some simple examples.\footnote{See \cite{DonThom} for a pioneering and illuminating discussion of how to find such analogs. See Nekrasov's thesis \cite{NekThesis} for a master physicist's view on holomorphic field theories, before he  reconfigured our understanding of much of gauge theory.}
To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
we describe them in several ways: 
in terms of PDE and action functionals but also as moduli spaces.
We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
and see \cite{AlfonsiYoung} and \cite{Steffens23} for recent work on this topic.

@@

We will start with $M$ being a Riemann surface for simplicity.
Consider the action functional
\beqn
\label{eqn: 1d betagamma}
\int \beta \wedge \dbar \gamma
\eeqn
where $\beta$ is a $(1,0)$-form on $M$.%\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
%which we now think about as having its own degrees of freedom. 
%\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
so that $\beta$ should be a holomorphic $1$-form.

@@

Derived geometry is the mathematical version of BV formalism.
From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
\[
T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\Omega^1_{hol}),
\]
where $\Omega^1_{hol}$ is the sheaf of holomorphic one-forms.

@@

The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite[Chapter 3]{Polchinski}.
There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
To recover the full boson, one must couple the chiral and anti-chiral sectors.
See \cite{Kapustin:2005pt,GGW} for more details.~\hfill$\Diamond$
\end{rmk}

@@

From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle
\[
T^*[-1] \Map_\dbar(M,N) ,
\]
where $\Map_\dbar(M,N)$ is the derived stack of holomorphic maps $M \to N$.
This is a natural space to study in complex geometry.

@@

\begin{rmk}
Holomorphic BF theory exhibits some interesting properties at the quantum level,
at least perturbatively.
For example, in \cite[\S3.2]{BGKWWY} it is shown that on $X = \C^2$ 
the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
More precisely, to first-order in perturbation theory, 
the divergence-free component of the stress tensor is rendered cohomologically trivial at one-loop in perturbation theory.
In other words, the quantum theory appears to be totally ``invariant'' under divergence-free vector fields,
although not all vector fields (as in the case of a TFT).
\end{rmk}

It is possible to formulate holomorphic versions of higher abelian gauge theories,
associated to moduli spaces of holomorphic $k$-gerbes with connection, see \cite{SWtensor,BWfive}.

@@

There is a higher-dimensional analog of the chiral sector of the scalar field.
Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
(When $n=0$ and $X$ is simply a Riemann surface, 
this constraint is automatic.)
The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
\eeqn
where $C \in \Omega^{2n+1}(X)$.
For more details we refer to~\cite{GRW_WZW}.

The reader may (and should) be concerned with the apparent ``non-local'' form of the action functional in \eqref{eqn:scalar1}.
This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint~\cite{CLbcov}.

@@

Any theory of gravity involves, in part, metric structure on a given manifold,
so that solutions to the equations of motion produce metrics satisfying a PDE. 
For a perturbative gravity theory,
one studies deformations of some metric structure on a manifold.
There is a holomorphic avatar of this situation: deformations of complex structure. 
The first appearance of such a theory was motivated by topological string theory and involves complex structures on Calabi--Yau threefolds~\cite{BCOV}.
It is known \textit{Kodaira--Spencer gravity} or the Kodaira-Spencer field theory,
due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
It has been pursued mathematically by Costello and Li as an approach to the quantum higher genus $B$-model, starting with \cite{CLbcov} and continuing in a series of papers.
In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
here we focus just on the most familiar three-dimensional version.
%The fields consist of pairs $(\mu, \eta)$ where
%\begin{align*}
%\mu & \in \Omega^{0,1}(X, \T_X) \\
%\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
%\end{align*}
%The action functional is
%\beqn
%\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
%\eeqn
%where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega$ the holomorphic volume form.
The primary field of Kodaira-Spencer theory is 
\beqn
\mu \in \Omega^{0,1}(X,\T_X),
\eeqn 
a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
A constraint is imposed on these sections:
we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
\[
{\rm div}_\Omega(\mu) = 0,
\]
i.e., its divergence vanishes.
In short, the fields are divergence-free vector fields.
The classical equation of motion is 
\beqn
\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
\eeqn
where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
Formulating the action functional to obtain this equation of motion is a little involved, 
and we refer to \cite{CLbcov} for a systematic discussion.

@@

This section offers a bridge from theories of physical interest to holomorphic field theories,
and hence may be of particular interest to physicists.
In his work on Donaldson invariants of four-manifolds, Witten introduced the idea of a topological twist of a supersymmetric field theory \cite{WittenTwist}.
The topological twist of a supersymmetric field theory (when it exists) can be attacked mathematically using the path integral.
A key feature, however, of topological field theories is that they are amenable to a functorial paradigm.
This firmly establishes their meaning and importance within pure mathematics.
Slightly after Witten's work, the first shadows of what would later be called \textit{holomorphic twists} of supersymmetric field theories appeared, see \cite{Johansen:1994aw,Johansen:1994ud,NekThesis,Losev:1996up,Losev:1995cr,Johansen:2003hw,Eager:2018oww}. 
Originally, this work did not garner the same attention as the parallel works on topological twists; especially in mathematics.
Much later, Costello introduced the precise notion of a holomorphic twist, and focused on examples in dimensions two and four \cite{CosSUSY}.
The characterization of all holomorphic, topological, and mixed holomorphic-topological theories of Yang--Mills type in dimensions $2 \leq d \leq 10$ appears in \cite{ESW}.
Holomorphic twists of more exotic quantum field theories, such as theories of supergravity and higher form gauge fields, have recently been studied in \cite{CLsugra,SWtensor,SWpure,Raghavendran:2021qbh,Eager:2021ufo,Garner:2023wrc}.

@@

By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
The classification of twisting supercharges is a completely algebraic question:
see~\autocite{EllSaf} for a complete classification in dimensions from $1$ to~$10$.

@@

If a classical field theory $\cT$ has $\ft$ as a symmetry, 
then a choice of twist $\cQ$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^\cQ$.
If $S$ denotes the action functional of $\cT$, then the action functional $S^\cQ$ of $\cT^\cQ$ has the form
\[
S^\cQ(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(\cQ \cdot \varphi \right) + \cdots 
\]
where the deformation arises from how $\cQ$ acts on the theory 
(the $\cdots$ leaves room for terms non-linear in $\cQ$).
For a systematic discussion of how the twisted theory is defined, 
we refer to~\autocite{CosSUSY, ESW}.

@@

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CLbcov, CLtypeI}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three complex dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
Holomorphic field theory has also appeared in applications to (twisted) holography through the lens of Koszul duality, see \cite{CLsugra, CGholography, CostelloPaquette}.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall:2001dx, Berkovits:2005bt}, see also \cite{Eager:2018dsx,perspectives}, starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
Such work can be viewed as extending (and enhancing) the original Penrose correspondence which relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose:1969ae, Penrose}---see \cite{adamo2018lecturestwistortheory} for a modern review.
See \cite{Mason, Mason_2009, CostelloTwistor,Bittleston_2023,garner2024scatteringtwistoriallinedefects} for recent work on the twistor correspondence in QFT.
\end{itemize}

We recommend \cite{bah2024panoramaphysicalmathematicsc} for more discussion and references.

@@

There are some features of this example that we would like to foreground. 
First, the commutative algebra arises as functions on a {\em symplectic} space,
which is the usual mathematical setting for classical mechanics (aside from more subtle situations that require Poisson geometry).
Second, the symplectic form $\omega = \d x \wedge \d p$ equips this algebra 
with a Poisson bracket where $\{ x, p \} = 1$,
which controls the deformation to the Weyl algebra: following Dirac, we promote the Poisson relation to a commutator relation.
These two features motivate the deformation quantization problem: 
given a symplectic (or Poisson) manifold,
describe deformations of its commutative algebra of functions to an associative algebra with the requirement that, to first order,  the commutator recovers the Poisson bracket.
Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics.

Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\ref{s:factinqft}), 
and it might help the reader to bear in mind a variant of this question:
given a classical holomorphic field theory, what are the natural deformations of its algebra of functions?
Many of the results we discuss later can be seen as generalizations of phenomena associated with deformation quantization.

@@

%\brian{something about states}
%So far we've recalled how quantization looks like for algebras.
%There is also a quantization for modules.
%Let $L \subset M$ be a Lagrangian submanifold.
%Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
%The Fock module $F(L)$ associated to $L$ is defined to be the quotient of 
%
%\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}

\subsection{A loopy version: the algebra of modes}

@@

At the level of action functionals, 
we can integrate $S_{2d}(\phi)$ over the angular coordinate to obtain the following formal sum of one-dimensional action functionals
\beqn
S_{red}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
\eeqn 
Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.

>>>>

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}

@@

\def\brian#1{{\textcolor{blue!75!red}{BW: {#1}}}}
\def\owen#1{{\textcolor{violet!50!black}{OG: {#1}}}}

@@

\owen{mention some history (e.g., Manin, Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, Kapranov, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}

\owen{Notation to explain: dg = differential graded, PDE = partial differential equations}

@@

\owen{Test references:} \cite{CG1,ManFrob}

@@

A physical motivation comes from supersymmetric field theories, 
which (loosely speaking) are theories on $\RR^n$ whose symmetries include not only the isometries of $\RR^n$, but an extension to a super Lie group known as a super Poincar\'e group.
%The relevant extension is often labeled by $\cN=1, 2,$ and so on, 
%with larger $\cN$ denoting a bigger supergroup. 
Thanks to the enhanced symmetry, such theories can often be understood in greater detail than non-supersymmetric theories.
The relevance to this survey is that supersymmetric theories admit ``twists'' (in essence, deformations) that are holomorphic field theories, 
even when they do not admit twists to TFTs \cite{CosHol}. 
(The famed A- and B-models of mirror symmetry are TFTs produced by twisting supersymmetric thories.)
As an example, four-dimensional minimally supersymmetric Yang-Mills theory admits no topological twist, 
but it does admit a twist to holomorphic field theory whose moduli space is described, in part, by the moduli space of holomorphic $G$-bundles~$\RR \Bun_G(X)$.

@@

A community has formed, involving both mathematicians and physicists, to explore and exploit these relationships,
and it continues to grow as there is a lot to explore here.
Examples of efforts in this direction include \cite{PTVV}, \cite{FHK}, \cite{Keviny things}, \cite{GaiottoEtAl}, \cite{Paquette}, \cite{Vicedo}, \cite{BeemBZEtAl}, 
where our own background and interests (and unfortunately, our ignorance) have shaped this list.

The material below focuses on connections with this work,
and the examples from physics have a perturbative flavor.
We will not discuss important directions like mirror symmetry, the geometric Langlands program, the BPS/CFT correspondence, Donaldson-Thomas theory, or other areas that are more global or more directly geometric,
although we expect there are rich connections with the topics we do discuss.
Not including these topics is primarily because our core theme already swelled to more pages than we expected, 
because a concise discussion of any of those topics does not yet seem possible with respect to our theme,
and because of our lack of background in these areas.
We hope the ideas surveyed here do connect profitably to these topics.
\owen{Is that an overly negative paragraph?}

@@

@@

In physics, a classical field theory is usually described in terms of a few pieces of data:
\begin{itemize}
\item a manifold $M$ that plays the role of ``spacetime,''
\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
\item a system of PDE for the fields, known as the equations of motion.
\end{itemize}
These equations of motion are variational: 
they are the Euler-Lagrange equations of an action functional on the space of fields,
so that solutions to these PDE are the critical points, in a sense, of some function.
In practice an action functional is a formal expression, 
written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
A few examples will illuminate this sketch.

@@

For a systematic introduction to classical field theory, 
in a style amenable to a complex geometer,
we suggest \cite{FreedDeligne}.
There are many other sources, such as \cite{}, because classical field theory is an old and deep subject.
Recently there is an effort to revisit field theory with insights from derived geometry.
See \cite{AlfonsoYoung?} for motivation and overview, 
but for a detailed development, see \cite{Steffens}.
In Section~\ref{sec: pert dfn} we offer a sharp definition well-suited to perturbative field theory 
(i.e., studying formal deformations of a fixed solution to the equations of motion),
which we will use to produce examples of higher algebras.

\subsection{Examples}
\label{sec: ex of theories}

@@

There are holomorphic versions of all these basic types, 
and we now spell out some simple examples.\footnote{See \cite{Donaldson Thomas} for a pioneering and illuminating discussion of how to find such analogs.}
To give the readers --- possibly a mixed audience of mathematicians and physicists --- some feel for the examples, 
we describe them in several ways: 
in terms of PDE and action functionals but also as moduli spaces.
We do not offer a thorough justification of the dictionary, for which see \cite{CosSUSY} for a wonderful and motivating exposition,
and see \cite{AlfonsoYoung} and \cite{Steffens} for recent work on this topic.

@@

We will start with $M$ being a Riemann surface for simplicity.
Consider the action functional
\beqn
\label{eqn: 1d betagamma}
\int \beta \wedge \dbar \gamma
\eeqn
where $\beta$ is a $(1,0)$-form on $M$.\footnote{It can be viewed as a Lagrange multiplier for the field $\del \Bar{\gamma}$, 
which we now think about as having its own degrees of freedom. 
\owen{I don't understand this use of the term Lagrange multiplier. Let's discuss!}}
Note that this action functional also imposes the equation of motion $\dbar \beta = 0$,
so that $\beta$ should be a holomorphic $1$-form.

@@

Derived geometry is the mathematical version of BV formalism.
From this point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
\[
T^*[-1] \Map_\dbar(M,\CC) = \RR\Gamma(M,\cO) \times \RR\Gamma(M,\cT^{*{1,0}}),
\]
a rather natural space to study in complex geometry.

@@

The $\beta\gamma$-system also plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.\owen{More precise location?}
There is likewise a complex-conjugate $\Bar{\beta}\Bar{\gamma}$-system encoding the antichiral sector of the free boson.
To recover the full boson, one must couple the chiral and anti-chiral sectors.
See \cite{Kapustin,GGW} \owen{Where?} for more details.~\hfill$\Diamond$
\end{rmk}

@@

From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
\[
T^*[-1] \Map_\dbar(M,N) 
\]
a rather natural space to study in complex geometry.

@@

\begin{rmk}
Holomorphic BF theory exhibits some interesting properties at the quantum level,
at least perturbatively.
For example, in \cite[\S3.2]{semichiral} it is shown that on $X = \C^2$ 
the perturbative quantization of holomorphic BF theory is almost a topological field theory. 
More precisely, to first-order in perturbation theory, 
the divergence-free component of the stress tensor is rendered cohomologically trivial at one-loop in perturbation theory.
In other words, the quantum theory appears to be totally ``invariant'' under divergence-free vector fields,
although not all vector fields (as in the case of a TFT).
\end{rmk}

It is possible to formulate holomorphic versions of higher abelian gauge theories,
associated to moduli spaces of holomorphic $k$-gerbes with connection.
\owen{Should we elaborate or just stop with a reference?}

@@

There is a higher-dimensional analog of the chiral sector of the scalar field.
Let $X$ be a complex manifold of dimension $2n+1$, i.e., odd.
The fields are the $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ that satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
(When $n=0$ and $X$ is simply a Riemann surface, 
this constraint is automatic.)
The action functional is $\int_X \alpha \dbar(\del^{-1} \alpha)$, the same as~\eqref{eqn:scalar1}.
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X \d C \wedge \star \d C , 
\eeqn
where $C \in \Omega^{2n+1}(X)$.
For more details we refer to~\cite{GRWwzw}.

The reader may (and should) be concerned with the apparent `non-local' form of the action functional in \eqref{eqn:scalar1}.
This can be made rigorous by cohomologically resolving the condition that $\alpha$ be $\del$-closed, rather than strictly imposing the constraint \cite{CLbcov1}.

@@

Any theory of gravity involves, in part, metric structure on a given manifold,
so that solutions to the equations of motion produce metrics satisfying a PDE. 
For a perturbative gravity theory,
one studies deformations of some metric structure on a manifold.
There is a holomorphic avatar of this situation: deformations of complex structure. 
The first appearance of such a theory was motivated by topological string theory and involves complex structures on Calabi--Yau threefolds~\cite{BCOV}.
It is known \textit{Kodaira--Spencer gravity} or the Kodaira-Spencer field theory,
due to its relationship with deformation of complex structures.\footnote{Kodaira and Spencer's work was an important initial clue in the relationship between deformation theory and dg Lie algebras.}
It has been pursued mathematically by Costello and Li \cite{CLbcov1,CLbcov2,LiThesis} as an approach to the quantum higher genus $B$-model.
In these works, Costello and Li also provide a generalization of the theory that makes sense in any complex dimension; 
here we focus just on the most familiar three-dimensional version.
%The fields consist of pairs $(\mu, \eta)$ where
%\begin{align*}
%\mu & \in \Omega^{0,1}(X, \T_X) \\
%\nu & \in \Omega^{0,n-2}(X, K_X \otimes \T^*_X) .
%\end{align*}
%The action functional is
%\beqn
%\int_X \left(\eta \dbar \mu + \frac12 \eta [\mu,\mu]\right)
%\eeqn
%where $[\mu, \mu] \in \Omega^{0,2} (X, \T_X)$ stands for the Lie bracket of holomorphic vector fields extended to the Dolbeault valued sections of $\T_X$ in the natural way.

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega$ the holomorphic volume form.
The primary field of Kodaira-Spencer theory is 
\beqn
\mu \in \Omega^{0,1}(X,\T_X),
\eeqn 
a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
A constraint is imposed on these sections:
we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
\[
{\rm div}_\Omega(\mu) = 0,
\]
i.e., its divergence vanishes.
In short, the fields are divergence-free vector fields.
The classical equation of motion is 
\beqn
\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
\eeqn
where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket.\footnote{On vector fields, $[-,-]_{SN}$ is simply the Lie bracket, and it is the natural multilinear extension to polyvector fields.}
The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
Formulating the action functional to obtain this equation of motion is a little involved, 
and we refer to \cite{CLbcov1} for a systematic discussion.

@@

This section offers a bridge from theories of physical interest to holomorphic field theories,
and hence may be of particular interest to physicists.

@@

By a {\em supercharge}, one means an odd supertranslation $\cQ \in \ft$, and
a {\em twist} is a (nonzero) supercharge $\cQ$ such that $[\cQ,\cQ] = \cQ^2 = 0$. 
The classification of twisting supercharges is a completely algebraic question:
see~\autocite{ESsusy} for a complete classification in dimensions from $1$ to~$10$.

@@

If a classical field theory $\cT$ has $\ft$ as a symmetry, 
then a choice of twist $\cQ$ determines a deformation of the theory that we call a {\em twisted supersymmetric theory} $\cT^\cQ$.
If $S$ denotes the action functional of $\cT$, then the action functional $S^\cQ$ of $\cT^\cQ$ has the form
\[
S^\cQ(\varphi) = S(\varphi) + \int_{\RR^d} \varphi  \left(\cQ \cdot \varphi \right) + \cdots 
\]
where the deformation arises from how $\cQ$ acts on the theory 
(the $\cdots$ leaves room for terms non-linear in $\cQ$).
For a systematic discussion of how the twisted theory is defined, 
we refer to~\autocite{CostelloHolomorphic, ESW}.

@@

There are many other appearances of holomorphic field theories in the context of supersymmetry.
Here is a (very) non-exhaustive list:
\begin{itemize}
\item Topological string theories yield rich classes of holomorphic field theories, as target space field theories. 
For instance, the topological B-model on a Calabi--Yau threefold $X$ leads to Kodaira--Spencer theory on $X$, as proposed in \cite{BCOV} using the framework of closed string field theory. 
The perspective of Kodaira--Spencer theory as a holomorphic field theory has been explored with great success by Kevin Costello and Si Li \cite{CL1, CL2, CL3}.
\item
It is possible to make sense of Kodaira--Spencer theory outside of three dimensions.
In \cite{CLsugra}, Costello and Li have argued for conjectural descriptions of twists of supergravity and superstring theories in terms of this more general version of Kodaira--Spencer theory.
\item The pure spinor formalism of Berkovits and Cederwall  \cite{Cederwall, Berkovits} starts with a field theory or string theory defined on the (sometimes singular) nilpotence variety of the super Poincar\'e algebra and then uses the action of supersymmetry to produce ordinary (non-twisted) supersymmetric field theories. 
Often, the theory on the nilpotence variety is holomorphic \cite{ESW,SWpure}. 
\item Similar in spirit to the pure spinor formalism is a systematic relationship between holomorphic field theories on (super) twistor space and ordinary (Riemannian) field theories.
For instance, the Penrose corresponds relates holomorphic BF theory on (super) twistor space associated to $\RR^4$ to the self-dual limit of (super) Yang--Mills theory \cite{Penrose, Kevins work..., other twistor literature}.
\end{itemize}
We recommend \owen{is there some other place to point?} for more discussion.

@@

There are some features of this example that we would like to foreground. 
First, the commutative algebra arises as functions on a {\em symplectic} space,
which is the usual mathematical setting for classical mechanics (aside from more subtle situations that require Poisson geometry).
Second, the symplectic form $\omega = \d x \wedge \d p$ equips this algebra 
with a Poisson bracket where $\{ x, p \} = 1$,
which controls the deformation to the Weyl algebra: following Dirac, we promote the Poisson relation to a commutator relation.
These two features motivate the deformation quantization problem: 
given a symplectic (or Poisson) manifold,
describe deformations of its commutative algebra of functions to an associative algebra with the requirement that, to first order,  the commutator recovers the Poisson bracket.
Thanks to Kontsevich \cite{KonDQ}, there is a beautiful answer to this question, which has spawned a mountain of fascinating mathematics (see, e.g., \owen{what?} as a starting place).

Our view on field theory is motivated by this perspective on quantum theory (we discuss it further in Section~\owen{ref the general overview}), 
and it might help the reader to bear in mind a variant of this question:
given a classical holomorphic field theory, what are the natural deformations of its algebra of functions?
Many of the results we discuss later can be seen as generalizations of phenomena associated with deformation quantization.

@@

\brian{something about states}
So far we've recalled how quantization looks like for algebras.
There is also a quantization for modules.
Let $L \subset M$ be a Lagrangian submanifold.
Then, functions $C^\infty(L)$ on $L$ are naturally a module for $C^\infty(M)$.
The Fock module $F(L)$ associated to $L$ is defined to be the quotient of

\owen{We should acknowledge the state perspective but it's not clear to me how much we should describe, in light of our development below.}

\subsection{A loopy version}

@@

At the level of action functionals, 
we can integrate $S_{2d}(\phi)$ over the angular coordinate to obtain the following formal sum of one-dimensional action functionals
\beqn
S_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \int  \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
\eeqn 
\owen{The $H$ got dropped. Should we reintroduct it?}
Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.
